\chapter{Introduction}
With the maturity of database technologies, many applications today collect and store data from all domains 
at unprecedented scale. For example, billions of 
social network users and their activities are collected in the form
of \emph{graphs}; Thousands of sensor ticks are collected every second
in the form of \emph{time series}; Hundreds of millions of spatiotemporal points
are collected as \emph{trajectories}.
Flooded by the tremendous amount of data, 
it is becoming increasingly critical to efficiently
conduct analytics to discover useful insights.
However, traditional SQL analytics, which comprises 
primary operations (e.g., partition, sorting and aggregation),
is unable to cope  with domain-specific analytics 
such as graph traversal and pattern detection. 
In practice, expressing these domain-specific 
analytics using SQL query often involves 
complex joins which are hard to optimize. 
In this thesis, we introduce the concept of \emph{neighborhood analytics} which
originates from the recognized SQL window functions. We study
the usage of \emph{neighborhood analytics} in different data domains
and design efficient algorithms to cope with today's big data.

%In this thesis, we explore an important type of 
%SQL analytics named \emph{window function}
%in supporting domain-specific analytics. 
%To this end, we generalize
%the window function to the \emph{neighborhood analytics} and propose
%three particular queries of such analytics in different domains.
%
%neighborhood-based domain-specific queries.
%Furthermore, we address the technical issues on how to
%efficiently process these neighborhood-based queries with regard to nowadays data sizes.
% efficiently
%process these neighborhood-based queries.

%which is expressive
%in many data domains. Furthermore, we address the technical issues on 

\input{chapter1/neighborhood_analytic}
\input{chapter1/thesis_scope}
\input{chapter1/contributions} 


\section{Thesis Organization}
The rest of the thesis is organized as follows: in Chapter 2, we review the literature related
to our proposed queries in different data domains.
In Chapter 3, we present the Graph Window Query on graph data. 
In Chapter 4, we present the $k$-Sketch Query on sequence data.
In Chapter 5, we present the General Co-Movement Pattern Query on trajectory data. 
Chapter 6 summarizes this thesis and highlights future directions.

\section{Published Material}
The research in this thesis has led to numerous publications. 

\begin{itemize}
	\item{The overview of the thesis has been published in SIGMOD Ph.D. Symposium.\\
		\textbf{Qi Fan}, Kian-Lee Tan. Towards Neighborhood Analytics. Proceedings of the ACM SIGMOD on PhD Symposium, 2015
	}
	\item{The work in Chapter 3 appears in DASFAA 2016.\\
		\textbf{Qi Fan}, Zhengkui Wang, Chee-Yong Chan, Kian-Lee Tan. Towards Window Analytics over Large-Scale Graphs. International Conference on Database Systems for Advanced Applications, 2016
	}
	\item{The finding in Chapter 4 have been submitted for publication.\\
		\textbf{Qi Fan}, Yuchen Li, Dongxiang Zhang, Kian-Lee Tan. Discovering Newsworthy Themes From Sequenced Data: A Step Towards Computational Journalism.
	}
	\item{The work in Chapter 5 has been accepted in VLDB 2017.\\
		\textbf{Qi Fan}, Dongxiang Zhang, Huayu Wu, Kian-Lee Tan. A General and Parallel Platform for Mining Co-Movement Patterns over Large-scale Trajectories. Proceedings of the VLDB Endowment, 2017
	}	
\end{itemize}

%The overview of the thesis has been published in:
%
%Qi Fan, Kian-Lee Tan. ``Towards Neighborhood Analytics.'' \emph{Proceedings of the ACM SIGMOD on PhD Symposium}, 2015
%
%The work in Chapter 3 appears in:
%
%Qi Fan, Zhengkui Wang, Chee-Yong Chan, Kian-Lee Tan. ``Towards Window Analytics over Large-Scale Graphs.'' \emph{International Conference on Database Systems for Advanced Applications}, 2016
%
%The findings in Chapter 4 have been submitted for publication.
%
%The work in Chapter 5 has been accepted in:
%
%Qi Fan, Dongxiang Zhang, Huayu Wu, Kian-Lee Tan. ``A General and Parallel Platform for Mining CoMovement Patterns over Largescale Trajectories.'' \emph{Proceedings of the VLDB Endowment}, 2017