\chapter{Literature Review}
Our proposed neighborhood based queries are inspired
by the usefulness of window functions in SQL analytics~\cite{zemke2012s}.
A window function in SQL specifies a set of partitioning attributes 
$A$ and an aggregate function $f$.
Its evaluation first sorts input records based on $A$ to form
overlapped partitions for each record. And then, $f$
is evaluated for every partition and the aggregate result is associated
with the corresponding records.
%Its evaluation first partitions the input records based on $A$ to compute 
%$f$ for each partition, and each input record is then associated with the aggregate 
%value corresponding to the partition that contains the record.
Several optimization techniques~\cite{bellamkonda2013adaptive,cao2012optimization }
have been developed to evaluate complex SQL queries 
involving multiple window functions.

However, the semantic and evaluation of the window function are restricted.
 In SQL window functions, tuples need to be sorted in order to form individual partitions (i.e., windows).
In fact, such a need is hard to meet in other data domains. Therefore, optimization techniques
that are developed for the relational model become inapplicable in other data domains. 
Nevertheless, there are quite a few works that are related to our proposed neighborhood based
queries and we review them in this section. 

%are very different between relational and graph contexts.
%Specifically, the partitions (i.e., subgraphs) associated with GWFs are not necessarily disjoint; thus,
%the evaluation techniques developed for relational context \cite{cao2012optimization, bellamkonda2013adaptive} are not applicable to GWFs. %\remark{\cite{bellamkonda2013adaptive} focuses on utilizing partition to parallel window processing, and \cite{cao2012optimization} focuses on leveraging sorting among windows. However sorting and partitioning are no longer exists in GWFS, thus, their work are not applicable}

\input{chapter2/rw-graph}
\input{chapter2/rw-sketch}
\input{chapter2/rw-trajectory}