\begin{acknowledgements}
I could not have completed this thesis without the help and support of many people.
It is my great pleasure to take this opportunity to thank all of them.
%
%Hereby, I would like to express my deepest gratitude to many people without whom this
%thesis would not have been completed.

First and foremost, I would like to express my utmost appreciation to 
my supervisor, Prof.~Kian-Lee Tan. Throughout my doctoral study, I have
received innumerable guidance and inspirations from him. His knowledgeable
insights play an important role in completing this thesis. As
a supervisor, he not only imparts me the rigorous research attitude
but also exemplifies a strong personality with
humility and gentleness. 
I would also like to mention his provision of the research assistant position which
sponsors me for the fifth year study. It is my privilege to be his student.

Second, I would like to deeply thank Prof.~Anthony K.~H.~Tung, Prof.~Shui-cheng Yan 
and Prof.~Roger Zimmermann for constituting my thesis advisory committee. 
I appreciate their efforts and time in monitoring and guiding my research with
inspiring comments. 


Third, I would like to especially thank Prof.~Zhengkui Wang and Prof.~Dong-xiang Zhang.
Prof.~Wang guided me on my first work which was a good starting point.
Prof.~Zhang has closely collaborated with me during my doctoral study. They
both generously shared me with the valuable knowledge on technical development 
and critical writing, which strengthened 
the technical quality and
literature presentation of my thesis.
I would not forget the assistance from my collaborators: Professor Chee-Yong Chan,
Dr.~Yuchen Li and Dr.~Huayu Wu. They have spent a lot of their precious time to greatly improve
our papers. It is fruitful to work with them.

Furthermore, I would like to thank NUS Graduate School of Integrative of Science and
Engineering (NGS) for offering me the scholarship.

Next, I feel lucky to have many friends during my academic
pursuit. They are Prof.~Zhifeng Bao, Dr.~Qian Xiao, Dr.~Htoo Htet Aung,
Dr.Long Guo, Dr.~Yong Zeng, Dr.~Zong Zeng, Dr.~Jingbo Zhou, Dr.~Yuxin Zheng, Yingjun Wu, Wentian Guo,
Yanhao Wang, Mo Sha, Qing Liu, Meiying Li, Qi Guo and Jiangwei Zhang. I would also 
like to thank my friends in Database Basketball Group %and Database Foosball Group
as we have shared wonderful memories.

Last but not least, the most special gratitude is reserved for my beloved family: my parents Xiaoquan Fan and Jiangrong Qi,
my parents-in-law Guangchen Cui and Yumei Zhang, and my dearest wife Sophia Xiang Cui.
Their unconditional support, persistent accompaniment, and consistent love
sustain me through the otherwise grueling Ph.D.~study.

%which has sustained me through the otherwise grueling period of my
%doctoral study
%
%
%through the otherwise grueling Ph.D.~study.

%My most appreciation is for my dearest wife Sophia Cui, 
%who provides me persistent accompany and love through the otherwise grueling Ph.D.~period.
%First and foremost, I would like to express my most profound gratitude to
%my supervisor, Prof. Beng Chin Ooi. Without him, I would not be able to
%complete my PhD program successfully. I was not from top university and
%did not come with very strong foundation and programming skills when I was
%admitted to the PhD program. I sincerely thank Prof. Ooi for his patience,
%guidance and support that helped me get through tough times and shape my
%research skills. I also thank him for offering me the opportunities to visit
%research labs and collaborate with accomplished researchers. It has been my
%great honor to be his student
%
%I would like to express my heartfelt gratitude and appreciation for his invaluable guidance
%and inspiration in this research, his moral support and encouragement during the duration
%of my Ph.D study. It is a privilege to work under him, and he has set a good example to
%me in many different ways. His insights and knowledge in this area play an important
%role in completing this thesis. As a supervisor, he shows me not only how to be a good
%researcher with rigorous research attitude, but also how to build a good personality with
%humility and gentleness. All that I have learned from him will be of great influence for
%my research and my entire life.
% 
%
%This thesis would not have been completed without the support of many people. I
%would like to reserve this section to express my gratitude to all of them.
%
%
%I would hereby express my gratitude to the people that have been ... without whom this thesis cannot be accomplished. 
%
%My utmost gratitude goes to my main supervisor, Prof. Kian-Lee Tan, for his constant and painstaking efforts in inspiring me to explore
%beyond the boundary of my research topic during my candidature. It has been a
%remarkable experience to conduct research under Professor Tan's guidance. During
%the time, he has shared much of his experience, knowledge and wisdom to me, which
%will surely benefit every aspect of my life. Regarding to research, he has always taught
%me to zoom in and zoom out when solving a particular problem, and this insight had
%deep impact on my research. Prof. Tan also provided me with many opportunities to
%stay in touch and collaborate with both local and global prestigious researchers which
%were invaluable experiences and broadened my horizon. I would also like to sincerely
%thank my TAC members, Prof. Anthony Tung, Prof Roger Zimmermann and Prof. Shuicheng Yan for the valuable guidance and support
%during my Ph.D. study. 
%
%I have been fortunate to work with these brilliant people
%who are generous with their time and friendship. My special thanks also go to my dear fellow colleagues. Without them, I would not have had such a meaningful Ph.D. life.
%Thank them for bringing me so many fond memories. I am also grateful to all the
%other staffs, fellow colleagues and friends in the Robotics Research Lab, the Social
%Robotics Lab and Advanced Robotics Center for their companionship, generous help
%and collaborations.
%
%I am also very grateful to National University of Singapore for providing me with a great opportunity and financial support to pursue my Ph.D. degree.
%
%Last but not least, I wish to thank my family, especially my parents and parents in-law, providing me the freedom to pursue my dream. My preserved thanks always goes to my wife Sophia, who consistently stands by me and give priceless support.
\end{acknowledgements}